Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-16 manuscript.tex

Some experimental results show the emergence of synchrony, for instance in motor cortical function~\citep{riehle_spike_1997}. Interestingly, these authors showed that ``accurate spike synchronization occurred in relation to external events (stimuli, movements) and was commonly accompanied by discharge rate modulations but without precise time locking of the spikes to these external events. Spike synchronization also occurred in relation to purely internal events (stimulus expectancy), where firing rate modulations were distinctly absent. These findings indicate that internally generated synchronization of individual spike discharges may subserve the cortical organization of cognitive motor processes.'' Moreover, such emergence could change over the learning period involved in learning a task~\citep{kilavik_long-term_2009} and showed some tuning to movement direction and reaction time~\citep{grammont_spike_2003}. It is important to note that synchronous events tend to lock to spatio-temporal patterns of neural activity called \href{https://en.wikipedia.org/wiki/Local_field_potential}{LFP} beta waves~\citep{denker_lfp_2018} and were also extended to larger assemblies using statistical methods~\citep{torre_asset_2016} (see Section~\ref{sec:detection} for further details). \change[Antoine]{}{Synchronicity is also an interesting proposition to explain how the relatively weak thalamo-cortical synapses are able to drive cortical neurons. Among different explanations concerning neuromodulation and other mechanisms, a synchronous activity at the synaptic level }Note also that synchronicity may explain some unintuitive results. Indeed, it has been shown that thalamo-cortical synapses are relatively weak compared to the amount of intracortical activity. However, this pathway is sufficient to drive the cortex, as this input is more often synchronously active, allowing it to more efficiently drive cortical neurons~\citep{bruno_cortex_2006}.

>>>>

Some experimental results show the emergence of synchrony, for instance in motor cortical function~\citep{riehle_spike_1997}. Interestingly, these authors showed that ``accurate spike synchronization occurred in relation to external events (stimuli, movements) and was commonly accompanied by discharge rate modulations but without precise time locking of the spikes to these external events. Spike synchronization also occurred in relation to purely internal events (stimulus expectancy), where firing rate modulations were distinctly absent. These findings indicate that internally generated synchronization of individual spike discharges may subserve the cortical organization of cognitive motor processes.'' Moreover, such emergence could change over the learning period involved in learning a task~\citep{kilavik_long-term_2009} and showed some tuning to movement direction and reaction time~\citep{grammont_spike_2003}. It is important to note that synchronous events tend to lock to spatio-temporal patterns of neural activity called \href{https://en.wikipedia.org/wiki/Local_field_potential}{LFP} beta waves~\citep{denker_lfp_2018} and were also extended to larger assemblies using statistical methods~\citep{torre_asset_2016} (see Section~\ref{sec:detection} for further details). \change[Antoine]{}{Synchronicity is also an interesting proposition to explain how the relatively weak thalamo-cortical synapses are able to drive cortical neurons. Among different explanations concerning neuromodulation and other mechanisms, a synchronous activity at the synaptic level may be sufficient to elicit }Note also that synchronicity may explain some unintuitive results. Indeed, it has been shown that thalamo-cortical synapses are relatively weak compared to the amount of intracortical activity. However, this pathway is sufficient to drive the cortex, as this input is more often synchronously active, allowing it to more efficiently drive cortical neurons~\citep{bruno_cortex_2006}.
